Growing libraries of concepts with wake-sleep program induction

### 2018-07-30 nips_2018_author_response.tex
re- factored response

We thank reviewer three for suggesting additions to the related work. Our
revision will prominently highlight the work of Kitzelmann, Schmid and Katayama.

The \textsc{Igor} systems introduced by Kitzelmann and Schmid is a sophisticated
algorithm for analytical inductive programming that handles a certain classe of
programs, much like {Sketch} and {FlashFill} are sophisticated program
synthesiser for certain classes of programs. This also relates to an insightful
and suggestion for comparison by reviewer 2: FlashFill's DSL is fixed and
manually curated and enhanced for a specific class of problems, over which is
performs well at the loss of agility.

We see these line of work as orthogonal and complementary to that of SCC\@. Our
goal is to take a black-box synthesiser and learn how to solve a class of
problems. One could in principle replace our enumerative search based solver
with \textsc{Igor}, Sketch or \textsc{MagicHaskeller}. We chose however to
use a more generic and simple enumerative approach for it allows us to apply SCC
to a diverse spread of problems: functional programming exercises, text editing,
graphics programming and symbolic regressions from images.

@@

\subsubsection*{Reproducibility}

Our project --- including source code, data and automation scripts --- is
already available on \url{GitHub} and future revision will include a link to it
once the anonymity of the authors can be unveiled. No technical knowledge will
be required to reproduced the results.

>>>>

We thank reviewer three for suggesting additions to the related work. Our
revision will prominently highlight the work of Kitzelmann, Schmid and Katayama,
particularly Kitzelmann and Schmid, whose cognitive inspiration
is closely allied with our motivations.

Kitzelmann and Schmid's \textsc{Igor} systems are sophisticated
analytical inductive programming algorithms that handle certain classes of
problems, much like {Sketch} and {FlashFill} are sophisticated program
synthesizers for certain classes of programs.
We see these lines of work as orthogonal and complementary to that of SCC\@. Our
goal is to take a black-box synthesizer and then learn how to use it to solve a class of
problems. One could replace our enumerative synthesizer
with \textsc{Igor}, Sketch or \textsc{MagicHaskeller}. We chose however to
use a generic and simple enumerative approach because it allowed us to apply SCC
to a diverse spread of problems: functional programming exercises, text editing,
turtle graphics programming, and symbolic regression from images.

This also relates to an insightful
and suggestion for comparison by reviewer 2: FlashFill's DSL is fixed and
manually curated and enhanced for a specific class of problems, over which is
performs well at the loss of agility.

@@

\subsubsection*{Reproducibility}
Our source code is publicly available on GitHub,
and a link will be added upon publication (in NIPS or elsewhere),
along with the specific command lines  needed to run
the experiments in the paper.

%% Our project --- including source code, data and automation scripts --- is
%% already available on \url{GitHub} and future revision will include a link to it
%% once the anonymity of the authors can be unveiled. No technical knowledge will
%% be required to reproduced the results.
